Constructing the transition graphs of interacting hysterons

### 2022-06-09 Paper_draft.tex
Added overview figure for N=2, l=2 graphs
Added in-text reference to overview figure of N=2, l=2 graphs

@@

 We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ . However, not every avalanche is necessarily valid. This is because an avalanche may not contain any cycles: if an avalanche did contain a cycle, it would lead to an infinite loop. We must therefore impose that $S^{(2)} \neq S^{(0)}$. As a result, the number of avalanche options per transition is either two, one, or zero.\\
By extending one of the transitions ina  graph from length $l=1$ to length $l=2$, we modify its design inequalities (see SI). In particular, we change the relaxation inequalities that describe the stability of the state $S^{(1)}$. We also add a new set of relaxation inequalities so that the state $S^{(2)}$ is stable.\\

>>>>

    \includegraphics[width=0.5\textwidth]{N2l2_overview.png}
    \caption{All combinations of $l=2$ avalanches for one of the two base graphs for $N=2$ (top-left) graph, with indication of graphs that of which the design inequalities are solvable (green), solvable except for the final set of relaxation inequalities (orange) and unsolvable (red).}
    \label{fig:N2l2}

@@

 We see that every transition $S^{(0)}\rightarrow S^{(1)}$ in the base graph can be extended to a $l=2$ transition  $S^{(0)}\rightarrow S^{(1)}\rightarrow S^{(2)}$ in at most two ways, by choosing either $S^{(2)} = S^{(2+)}$ or $S^{(2)} = S^{(2-)}$ . We must check for each of these transitions that $S^{(2)} \neq S^{(0)}$, because an avalanche cannot contain any cycles. By then evaluating all combinations of valid avalanches, we obtain a list of candidate graphs for each base graph. An example for one of the $N=2$ base graphs is shown in Fig. \ref{fig:N2l2}. For the example shown, the base graph has four possible $l=2$ avalanches all associated with a different transition ($00\uparrow 01\uparrow 11$, $01\uparrow11\downarrow10$, $11\downarrow10\downarrow00$, and $10\downarrow00\uparrow01$), and therefore $2^4=16$ candidate graphs.\\
